---
title: "World Cup data analysis"
output: html_notebook
---

```{r}
source("WorldCup.R")
```

# France

```{r}
country <- "France"

statsFr <- getStats(country)
```

#### Appearances: `r I(statsFr$Appearances)`
#### Number of games played: `r I(statsFr$`Number of games played`)`
#### Goals for: `r I(statsFr$`Goals for`)`
#### Goals for/game: `r I(statsFr`Goals for per game`)`
#### Goals against: `r I(statsFr`Goals against`)`
#### Goals against/game: `r I(statsFr`Goals against per game`)`

# Brazil

```{r}
country <- "Brazil"

statsBr <- getStats(country)
```

#### Number of games played: `r I(statsBr[1,2])`
#### Goals for: `r I(statsBr[1,3])`
#### Goals for/game: `r I(statsBr[1,5])`
#### Goals against: `r I(statsBr[1,4])`
#### Goals against/game: `r I(statsBr[1,6])`

# Germany / West Germany

```{r}
country <- "West Germany (-1989)"

gamesDataWg <- getGamesFor(country)

# Gets goals for
goals <- getGoalsFor(gamesDataWg, country)


country <- "Germany"

gamesData <- getGamesFor(country)

print(paste("Games played: ", length(gamesData[,1]) + length(gamesDataWg[,1])))

# Gets goals for
goals <- goals + getGoalsFor(gamesData, country)

print(paste("Goals for: ", goals[1]))
print(paste("Goals against: ", goals[2]))

print(goals)

```
